Paper_Notes

### 2017-10-01 Paper_Notes.Rmd
Paper Notes Assignment 2, Microarray technology commit

@@

- Watson, J. D., and F. H. Crick. "Molecular Structure of Nucleic Acids;
a Structure for Deoxyribose Nucleic Acid." Nature 171, no. 4356 (April 25,
1953): 737-38

@@

>>>>

<style>
body {
text-align: justify}
</style>

@@

- Watson, J. D., and F. H. Crick. "Molecular Structure of Nucleic Acids;a Structure for Deoxyribose Nucleic Acid." Nature 171, no. 4356 (April 25, 1953): 737-38

@@

### Tumor Analysis Best Practices Working Group, 2004

- Tumor Analysis Best Practices Working Group. "Expression Profiling-Best Practices for Data Generation and Interpretation in Clinical Trials." Nature Reviews. Genetics 5, no. 3 (March 2004): 229-37.

The review written by the Tumor Analysis Best Practices Working Group attempts to provide recommendations for standardizing experimental design, probe-set algorithms, signal/noise assessments, and biostatistical methods for microarray technologies. It is important to develop a set of best practices since microarray technologies are widely used in clinical trials, both for differential diagnoses and monitoring of pharmacological efficacy. Their first discussion point regards the importance of appropriate experimental design. Replication in cross-sectional studies is important since the source of biological variability can confound many results. Preclinical animal testing may only need a few replicates whereas human samples require considerably more individuals per group due to their genetic heterogeneity. Tissue/cell heterogeneity is a major confounding variable in many micro-array experiments. The Working Group suggests normalization techniques based on bioinformatics methods, or isolating pure cell populations for expression profiling. Furthermore, a longitudinal experimental design provides greater power at lower numbers of replicates since each subject serves as their own control. Technical variability is the next discussion point the Working Group reviews. Methods for checking the purity of isolated RNA have been used for over three decade. The Working Group recommends that samples that do not meet the established criteria should be discarded. In addition, the development of standards would require all laboratories to use the same control RNA solution before data could be easily compared. The last point discusses the analysis and interpretation of collected data. Much of the debate in the field of bioinformatics about microarray interpretation revolves around signal/noise ratios. The Working Group states that each project will have its own signal/noise optimum, and, ideally, a signal/noise ratio should be optimized for each project. The recommendations the working group suggests should be followed and it would be interesting to read a follow-up to this review as it was published in 2004.

### Lipshutz et al. 1999
- Lipshutz, R. J., S. P. Fodor, T. R. Gingeras, and D. J. Lockhart. "High Density Synthetic Oligonucleotide Arrays." Nature Genetics 21, no. 1 Suppl (January 1999): 20-24.

This review article describes the fabrication, design, and specific applications of high-density synthetic oligonucleotide arrays created by the company Affymetrix, Inc. It should be noted that the review was written by employees of Affymetrix, Inc. The ability for these arrays to come to fruition was due to two key technologies: 1) the fabrication of hundreds of thousands of polynucleotides at high spatial resolution in precise locations on a surface and 2) the optimization of laser confocal fluorescence scanning. Affymetrix uses photolithography, the same method used to fabricate integrated circuits for electronics, to deposit oligonucleotide probes that match parts of the sequence of interest of known or predicted open readings frames of genetic material. To fabricate the array, light and light-sensitive masking agents are used to generate a sequence one nucleotide at a time across the entire array. Each applicable probe is selectively unmasked prior to bathing the array in a solution of a single nucleotide, then a masking reaction takes place and the next set of probes are unmasked in preparation for a different nucleotide exposure. After many repetitions, the sequences of every probe become fully constructed. One of the keys to this process is through probe redundancy where each array is constructed from a series of mismatch (MM) control probes that are identical to their perfect match (PM) probes, allowing some assessment of non-specific binding and performance of the probes. Overall, the Affymetrix oligonucleotide arrays allow robust measures of gene expression. The resolution allows one hundred million non-overlapping 30-mer probes spanning the entire human genome to fit on a 2x2 cm array. Furthermore, these arrays are designed based on sequence information, which eliminates the need for physical intermediates such as clones, PCR products, or cDNAs, which drastically reduces many sources of potential error.
